%-------------------------
% Resume in Latex
% Author : Charles-Olivier Ipperciel
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Charles-Olivier Ipperciel} \\ \vspace{1pt}
    \small 438-827-2307 $|$ \href{mailto:charlesolivieripperciel@gmail.com}{\underline{charlesolivieripperciel@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/coipp/}{\underline{linkedin.com/in/coipp/}} $|$
    \href{https://charlesoipperciel.github.io/PortfolioReact/}{\underline{charlesoipperciel.github.io/PortfolioReact}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Université de Sherbrooke}{Québec, Canada}
      {Master's Degree in Computer Science, Part-Time}{Starting Sep 2026 -- Aug 2028}
    \resumeSubheading
      {Université de Sherbrooke}{Québec, Canada}
      {Bachelor's Degree In Computer Science COOP Program}{Jan 2022 -- April 2025}
    \resumeSubheading
      {HEC Montréal}{Québec, Canada}
      {Bachelor's Degree in Business Administration, 2-Year Major}{Sep 2019 -- Dec 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Customer Success Manager}{Oct 2025 -- Present}
    {Institut du E-Commerce}{Hybrid}
    \resumeItemListStart
      \resumeItem{Ensuring our students are \textbf{well equipped} and helped throughout their e-commerce learning experience.}
      \resumeItem{This role focuses on \textbf{student support} and success in their e-commerce education journey.}
      \resumeItem{\textbf{Monitor} student progress and provide \textbf{personalized guidance} to enhance their learning outcomes.}
      \resumeItem{\textbf{Collaborate} with instructors and management to improve course content and student engagement strategies.}
      \resumeItem{Technologies: \textbf{Circle, Slack}.}
    \resumeItemListEnd

    \resumeSubheading
    {Buyer \& Full Stack Developer}{May 2025 -- Present}
    {A1 Imports}{Hybrid}
    \resumeItemListStart
      \resumeItem{Accepted full-time position at A1 Imports under the \textbf{A1 Arbitrage Division}.}
      \resumeItem{\textbf{Source} suppliers, \textbf{negotiate} contracts, and \textbf{ensure} timely deliveries.}
      \resumeItem{\textbf{Develop} sales forecasts to support \textbf{strategic} business growth.}
      \resumeItem{\textbf{Built} an application using \textbf{SP-API}, \textbf{React} and \textbf{Python} to automate tasks and improve efficiency.}
      \resumeItem{Technologies: \textbf{React, Python, Firebase, Amazon SP-API, Office Suite, Fidelio ERP}.}
    \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{May 2024 -- May 2025}
      {MEDomicsLab}{Hybrid}
      \resumeItemListStart
        \resumeItem{Developed and implemented \textbf{new features} for MEDomicsLab, an \textbf{open-source} AI healthcare platform.}
        \resumeItem{Enhanced machine learning tools, improved scalability, and implemented \textbf{MongoDB} to handle larger datasets.}
        \resumeItem{Worked on frontend \textbf{(React)} and backend \textbf{(Python)} for better database communication.}
        \resumeItem{Full-time internship transitioned into a \textbf{part-time role}.}
        \resumeItem{Technologies: \textbf{Python, MongoDB, React.js, Git}.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Developer}{Aug 2023 -- Dec 2023}
      {Sherweb}{Remote}
      \resumeItemListStart
        \resumeItem{Developed \textbf{new features} in the billing team, fixed \textbf{bugs}, and monitored/debugged software daily.}
        \resumeItem{Integrated the Braintree software for credit card processing, replacing Paysafe in a \textbf{C\#} codebase.}
        \resumeItem{Worked in an \textbf{Agile} environment with daily scrums.}
        \resumeItem{Technologies: \textbf{C\#, .NET, Azure DevOps, Datadog, Octopus, Git, MySQL}.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{Jan 2023 -- May 2023}
      {Qwatro Inc.}{On-site}
      \resumeItemListStart
        \resumeItem{Built an app for tracking employee hours at construction sites.}
        \resumeItem{Developed UI/backend in \textbf{Python} with \textbf{MongoDB} as the database option.}
        \resumeItem{Aided in \textbf{ERP} selection for digital transformation.}
        \resumeItem{Technologies: \textbf{Python, MongoDB, Git}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Vitopia – Visual Simulations of Computer-Biological Entities} $|$ \emph{C++, OpenGL, Git}}{260-Hour Project}
          \resumeItemListStart
            \resumeItem{Developing an AI 2D \textbf{shader-based} simulation to observe evolving organisms in complex societies.}
            \resumeItem{Models ecological behaviors, reactions to stimuli, and economic interactions.}
            \resumeItem{Project will be deployed online and available on \textbf{GitHub}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Coded Kingdom} $|$ \emph{Godot, Python, Aseprite, Git}}{130-Hour Project}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{pixel-based} game that teaches programming through interactive gameplay.}
            \resumeItem{Players must write code and execute it to advance their characters through the levels.}
            \resumeItem{This was one of my final bachelor's projects, with all code and the latest release available on \textbf{GitHub}.}
          \resumeItemListEnd


      \resumeProjectHeading
          {\textbf{Budgetly} $|$ \emph{React, Tailwind CSS, Firebase}}{Private Tool}
          \resumeItemListStart
            \resumeItem{Developed a private tool using \textbf{React} and \textbf{Tailwind CSS} to manage my personal budget.}
            \resumeItem{Implemented \textbf{Firebase} backend for secure data storage and real-time synchronization across devices.}
            \resumeItem{Created an intuitive user interface with modern design principles for efficient budget tracking and analysis.}
            \resumeItem{Features include expense categorization, budget goal setting, and comprehensive financial reporting.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Taskline} $|$ \emph{React, SP-API, Firebase, Make.com}}{Private Tool}
          \resumeItemListStart
            \resumeItem{Developed a private tool using \textbf{SP-API} to better utilize data from our seller central at work.}
            \resumeItem{Implemented automated data processing workflows using \textbf{Make.com} for seamless integration.}
            \resumeItem{Built a \textbf{React} frontend with \textbf{Firebase} backend to provide real-time analytics and insights.}
            \resumeItem{Streamlined business operations by centralizing seller central data and improving decision-making processes.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Insulin Dosage Calculator} $|$ \emph{React, Firebase, HTML/CSS, Git}}{Personal Project}
          \resumeItemListStart
            \resumeItem{Developed an application that calculates \textbf{insulin dosage} for newly diagnosed type 1 diabetes patients.}
            \resumeItem{This application is used by pediatric residents to verify their written calculation results at Fleurimont Hospital.}
            \resumeItem{Hosted and deployed on \textbf{Firebase}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C\#, C++, JavaScript, HTML/CSS, SQL (PostgreSQL), MongoDB (NoSQL).} \\
     \textbf{Librairies/Frameworks}{: React, Angular.} \\
     \textbf{Developer Tools}{: Git, Docker, Azure DevOps, Octopus, Datadog, CI/CD, Linux, Godot, Office Suite, Circle app, Slack.} \\
     \textbf{Video Editing}{: Adobe Premiere Pro, Adobe Photoshop, Pixaki (Pixel Art), Aseprite.} \\
     \textbf{Linguistics}{: Fluent in both spoken and written French and English.}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}